My title

### 2024-10-22 paper/paper.qmd
update

Forecasting election outcomes has become a critical endeavor in political science and public policy, as it not only informs campaigns and media coverage but also shapes voter perceptions. The ability to accurately predict the winner of a presidential election holds significant implications for political strategy, governance, and public trust in polling methodologies. In this context, leveraging aggregated polling data, or “poll-of-polls,” offers a more comprehensive and reliable prediction model, as it aims to reduce the biases and errors associated with individual polls (Blumenthal 2014; Pasek 2015).

This paper aims to explore the predictive power of a linear or generalized linear model using a poll-of-polls approach to forecast the winner of the upcoming US presidential election. The motivation behind this research stems from the persistent challenge of balancing sample biases, framing, and non-response rates, which can all impact the reliability of a single poll. By aggregating data from multiple polls, the goal is to create a robust and reproducible model that accounts for these discrepancies and better reflects voter sentiment.

To achieve this, the study focuses on a deep-dive analysis of a specific pollster, examining their methodology in detail. This analysis includes understanding the population, sampling frame, and recruitment process, as well as evaluating the strengths and limitations of their questionnaire design. Additionally, the paper proposes an idealized survey and methodology, imagining a scenario with a $100K budget to forecast the election outcome. This hypothetical scenario explores alternative approaches to survey design, data collection, and aggregation techniques.

This study is significant because it not only aims to build an effective model for election forecasting but also provides critical insights into the methodologies of polling organizations. The findings of this research can contribute to a more nuanced understanding of how polling data is collected and interpreted, ultimately improving the accuracy of election predictions.

The structure of the paper is as follows: first, the methodology for the forecasting model is presented; second, a detailed analysis of the chosen pollster is included in an appendix, followed by the idealized survey design and methodology. Together, these elements provide a comprehensive understanding of the challenges and opportunities in election forecasting using aggregated polling data.

@@

Potential for Non-response Bias: Despite efforts to mitigate it, non-response remains a concern, particularly among certain voter demographics who may be harder to reach through phone or online surveys.
Self-selection Bias in Online Surveys: The online component may disproportionately attract respondents who are more politically engaged, which could skew results.
By employing a multi-mode approach and adjusting for demographic imbalances through weighting, Emerson College Polling provides robust and timely data. However, like all polls, it is subject to limitations, particularly around non-response and self-selection biases​
\newpage

>>>>

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

@@

Potential for Non-response Bias: Despite efforts to mitigate it, non-response remains a concern, particularly among certain voter demographics who may be harder to reach through phone or online surveys.
Self-selection Bias in Online Surveys: The online component may disproportionately attract respondents who are more politically engaged, which could skew results.
By employing a multi-mode approach and adjusting for demographic imbalances through weighting, Emerson College Polling provides robust and timely data. However, like all polls, it is subject to limitations, particularly around non-response and self-selection biases​

## Idealized Methodology for US Presidential Election Forecast
This appendix outlines the methodology and design for conducting a U.S. presidential election forecast survey with a budget of $100,000. The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.

Methodology Overview
1. Sampling Approach
To ensure a representative sample of likely voters, I will use a stratified random sampling method based on demographic and voter turnout data from the U.S. Census and previous elections.

Target Population: U.S. citizens eligible to vote in the 2024 U.S. presidential election.
Sample Size: I plan to survey 3,500 respondents, providing a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results.
Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income. This ensures that each demographic group is represented proportionally to the U.S. population.
Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.
2. Recruitment of Respondents
I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.

Online Recruitment: Use targeted advertisements on social media platforms (e.g., Facebook, Instagram) and popular news websites. A portion of the budget will be allocated to recruiting via established online panel providers such as Qualtrics or YouGov.
Phone and SMS Polling: To capture voters who may not engage online, I will employ live phone interviews using Random Digit Dialing (RDD) and SMS text polls, ensuring coverage of both landline and mobile users.
In-Person Recruitment: In key battleground states, local fieldworkers will be deployed to recruit voters who may not be reached through digital or phone methods, ensuring a geographically diverse sample.
3. Data Validation and Quality Control
Data quality is crucial for accurate forecasting, and several measures will be implemented to ensure the validity of responses:\
Voter Verification: Respondents will be asked to confirm their voter registration status, and a subset of the sample will be cross-checked with voter databases to validate their responses.
Attention Checks: To minimize random or disengaged responses, I will include attention checks (e.g., questions asking respondents to select a specific answer) throughout the survey.
Duplicate Prevention: Respondent IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual.
Weighting: Post-stratification weighting will be applied to adjust for any demographic imbalances in the final sample. Weighting factors will be based on age, gender, race, education, and voting history to match U.S. population benchmarks.

4. Poll Aggregation and Forecasting Model
In addition to my own survey, I will aggregate data from other reputable pollsters to improve the accuracy of the forecast.

Poll Aggregation: I will collect data from publicly available polls (e.g., FiveThirtyEight, RealClearPolitics) and develop a weighted average based on the reliability of each poll, sample size, and recency.
Weighting by Pollster Quality: Pollsters will be rated based on their historical accuracy, sample sizes, and transparency in methodology. More reliable polls will be weighted higher in the aggregation model.
Predictive Modeling: I will use a Bayesian predictive model that incorporates current polling data, historical voting patterns, economic indicators, and other key variables to generate a probabilistic forecast of the election outcome.

5. Questionnaire Design
The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions. It will be short and simple, taking no more than 10 minutes to complete.
Survey Link
The survey has been implemented using Google Forms. Here is the link to access the survey:\
https://docs.google.com/forms/d/e/1FAIpQLSetY5pPLMYHn4YXF2uIxVNnCGUB1PRvyHbSd3HF3E6DdN2EkA/viewform

Budget Breakdown
Here is a proposed allocation of the $100,000 budget:\
Survey Platform and Software Costs: $5,000 for survey hosting on Google Forms and Qualtrics.
Recruitment Costs: $40,000 for online panel recruitment, social media ads, and targeted outreach.
Phone and SMS Polling: $20,000 to cover live phone interviews and SMS polling.
Fieldwork in Key States: $15,000 for in-person recruitment in battleground states.
Data Validation and Cleaning: $10,000 for voter verification, attention checks, and cleaning services.
Poll Aggregation and Modeling Tools: $7,000 for the development of a poll aggregation tool and Bayesian forecasting model.
Miscellaneous Costs: $3,000 for administrative costs, project management, and reporting.
